---
output: html_document
---

## Dhading School Survey: Plotting and Insights
In this document, we try to generate relavnt insights around schools from the Dhading Schools Survey, and also play with RMarkdown for storing this information

### Load required libraries
```{r}
# Load Libraries
library(tmap)
library(leaflet)
```

### Load files
The following two files will be loaded:
* ddng_poly: Which contains polygon information for all VDCs in Dhading
* ddng_sch: Which contains scjool level coordinates, as well as attribute data

```{r}
ddng_poly<-readRDS("data/ddng_poly.Rds")
ddng_sch<-readRDS("data/ddng_sch.Rds")

summary(ddng_sch@data)
```



### Plot maps

#### Plot 1: Distribution of schools by VDC

```{r}
ddng_poly_agg<-aggregate(x<-ddng_sch["no_students_total"], by=ddng_poly, FUN="length")
tm_shape(ddng_poly_agg)+tm_fill(col = "no_students_total", title="Total Schools Surveyed", palette="Blues") + tm_borders()

pal <- colorNumeric(
  palette = c("yellow","red"),
  domain = ddng_poly_agg$no_students_total
)

ddng_poly_agg %>% leaflet() %>% addTiles() %>% addPolygons(fillOpacity = .8,color = ~pal(no_students_total),weight = 0.5)%>%addMarkers(data=ddng_sch, popup=~as.character(ddng_sch$school_name),clusterOptions=markerClusterOptions() )


# ddng_poly_agg %>% leaflet() %>% addTiles() %>% addPolygons(fillOpacity = .8,fillColor = topo.colors(10, alpha = NULL),weight = 0.5)%>%addMarkers(data=ddng_sch, clusterOptions=markerClusterOptions() )

```




<!-- ddng_poly_agg %>% leaflet() %>% addTiles() %>% addPolygons(fillColor = topo.colors(10, alpha = NULL),popup=~vdc_label) -->
